Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Channel at the LHC with Multivariate Techniques

### 2015-11-30 paper/sec-mva.tex
Added plots of Higgs mass resolution

The post-MVA results for $S/\sqrt{B}$ and $S/B$ as a function of the cut
in the ANN output for each of the three categories are shown in
Fig.~\ref{fig:sb_mva}.
%
Note that the values of $S/\sqrt{B}$ and $S/B$
for $y_{\rm cut}=0$ correspond to the values at
the end of the cut-based analysis, see
the {\bf C2} row of Table~\ref{table:cutflow}.
%
Indeed, at the end of the cut based analysis $S/\sqrt{B}$ was
approximately
1.0, 0.5 and 0.5 for the boosted, intermediate and resolved
categories, as can be seen from Fig.~\ref{fig:sb_mva}.
%
The same applies to $S/B$.

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\begin{center}
\includegraphics[width=0.48\textwidth]{plots/ssb_noPU.pdf}
\includegraphics[width=0.48\textwidth]{plots/sb_noPU.pdf}
\caption{\small
  The values of the signal significance $S/\sqrt{B}$ and of the
  signal over background ratio $S/B$ for the boosted, intermediate
  and resolved categories as  function of the cut
  $y_{\rm cut}=0$ in the ANN output.
  %
  The $y_{\rm cut}=0$
  values correspond to the  cut-based analysis
  results from Table~\ref{table:cutflow}.
}
\label{fig:sb_mva}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

>>>>

The post-MVA results for $S/\sqrt{B}$ and $S/B$ as a function of the cut
in the ANN output for each of the three categories are shown in
Fig.~\ref{fig:sb_mva}.
%
Note that the values of $S/\sqrt{B}$ and $S/B$
for $y_{\rm cut}=0$ correspond to the values at
the end of the cut-based analysis, see
the {\bf C2} row of Table~\ref{tab:cutflow_noPU_1}.
%
Indeed, at the end of the cut based analysis $S/\sqrt{B}$ was
approximately
1.0, 0.5 and 0.5 for the boosted, intermediate and resolved
categories, as can be seen from Fig.~\ref{fig:sb_mva}.
%
The same applies to $S/B$.

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\begin{center}
\includegraphics[width=0.48\textwidth]{plots/ssb_noPU.pdf}
\includegraphics[width=0.48\textwidth]{plots/sb_noPU.pdf}
\caption{\small
  The values of the signal significance $S/\sqrt{B}$ and of the
  signal over background ratio $S/B$ for the boosted, intermediate
  and resolved categories as  function of the cut
  $y_{\rm cut}=0$ in the ANN output.
  %
  The $y_{\rm cut}=0$
  values correspond to the  cut-based analysis
  results from Table~\ref{tab:cutflow_noPU_1}.
}
\label{fig:sb_mva}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

### 2015-11-30 paper/sec-pileup.tex
Added plots of Higgs mass resolution

>>>>

Finally, it is interesting to compare how the Higgs peak mass resolution is degraded
in the case of PU.
%
In Fig.~\ref{fig:higgs-mass-resolution} we show the invariant mass distributions of the leading
    Higgs candidate in signal events for the resolved category, without
    PU (left plot) and with PU ($\la n_{\rm PU}\ra=80$+SK, right plot).
    %
    In both cases a Gaussian fit is used to determine the mass resolution.
    %
    In the case without PU, we find a mass resolution of about 8\%, corresponding
    to around 10 GeV for the Higgs mass.
    %
    This mass resolution arises both from the smearing we introduce to mimic detector
    effects as well as from ISR and FSR.
    %
    In the case of PU, the mass resolution is increased to around 11\%, corresponding to
    14 GeV.
    %
    These values are similar to the current and prospected mass resolutions in ATLAS and CMS.

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
  \begin{center}
    \vspace{-1cm}
  \includegraphics[width=0.49\textwidth]{plots/higgs_mass_res_noPU.pdf}
  \includegraphics[width=0.49\textwidth]{plots/higgs_mass_res_PU80.pdf}
  \caption{\small The invariant mass distributions of the leading
    Higgs candidate in signal events for the resolved category, without
    PU (left plot) and with PU ($\la n_{\rm PU}\ra=80$+SK, right plot).
    %
    In both cases a Gaussian fit is used to determine the mass resolution.
    %
    See text for more details.
}
\label{fig:higgs-mass-resolution}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Cut-flow}

The corresponding cut-flow tables in the case
of PU subtracted with SK, for $\la n_{\rm PU}\ra=80$,
are shown in Table~\ref{tab:cutflow_SKPU80_1},
for the total cross-sections, number of events expected and
signal significance at the HL-LHC, respectively.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
  \centering
  \scriptsize
  \input{tables/table_SKPU80_1.tex}
  $\,$ \\
  \vspace{0.5cm}
  \input{tables/table_SKPU80_2.tex}
  $\,$ \\
  \vspace{0.5cm}
    \input{tables/table_SKPU80_3.tex}
    \caption{\small
      Same as Table~\ref{tab:cutflow_noPU_1}, for the analysis
      including PU with $\la n_{\rm PU}\ra=80$ and SK subtraction.
      \label{tab:cutflow_SKPU80_1}}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-11-30 paper/sec-results.tex
Added plots of Higgs mass resolution

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
  \centering
  \begin{tabular}{|c|c|c|c|}
\hline
&  Boosted  &   Intermediate &  Resolved  \\
\hline
\hline
C0 &  Generator level &  Generator level & Generator level \\
\hline
C1a & $N_{\rm jets}^{R}\ge 2$ & $N_{\rm jets}^{r}\ge 2$, $N_{\rm jets}^{R}=1$  &
 $N_{\rm jets}^{r}\ge 4$ \\
 C1b & +$p_T$ cuts & +$p_T$ cuts
 & +$p_T$ cuts \\
 C1c & + rapidity cuts &  + rapidity cuts &
 + rapidity cuts \\
 C1d & + Mass-Drop tag required & $N_{\rm jets}^{R}=1$ with MDT  &
  Higgs reco possible \\
C1e & $m_H$ window cut & $m_H$ window cut & $m_H$ window cut  \\
\hline
C2 & $b$-tagging  &  $b$-tagging &  $b$-tagging \\
\hline
  \end{tabular}
  \caption{\small Details of the cut-flow of the present analysis in the boosted, intermediate
    and resolved categories.
    %
    See text for more details.
    \label{tab:cutflowdetails}
  }
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In Fig.~\ref{fig:histoBack} we show the decomposition of the background for one important kinematical
distribution, the $p_T$ of the leading reconstructed Higgs candidate, various background
components, for both the boosted and the resolved categories.
%
In the same figure we also show the results of the corresponding comparison
at the level of the $p_T^{hh}$ of the
reconstructed di-Higgs system.
%
The histograms correspond to the distributions at the end of the cut-based
analysis.
%
The results are consistent with those summarized in
Table~\ref{table:cutflowBack}: in the boosted case we see how $4b$ is the most important
component of the background, with $2b2j$ being of the same order of magnitude, while
for the resolved category we see that $2b2j$ dominates instead.
%
So the effect of the fakes is certainly important, but fortunately it is not a limiting factor
in the resolved category, the one that leads to higher signal significance.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
  \centering
  \begin{tabular}{|c|c|c|c|}
\hline
&  Boosted  &   Intermediate &  Resolved  \\
\hline
\hline
{\bf C0} &  Generator level &  Generator level & Generator level \\
\hline
{\bf C1a} & $N_{\rm jets}^{R10}\ge 2$ & $N_{\rm jets}^{R04}\ge 2$, $N_{\rm jets}^{R10}=1$  &
 $N_{\rm jets}^{R04}\ge 4$ \\
{\bf  C1b} & +$p_T$ cuts & +$p_T$ cuts
 & +$p_T$ cuts \\
 {\bf C1c} & + rapidity cuts &  + rapidity cuts &
 + rapidity cuts \\
 {\bf C1d} & + Mass-Drop tag required & $N_{\rm jets}^{R}=1$ with MDT  &
  Higgs reco possible \\
{\bf C1e} & $m_H$ window cut & $m_H$ window cut & $m_H$ window cut  \\
\hline
{\bf C2} & $b$-tagging  &  $b$-tagging &  $b$-tagging \\
\hline
  \end{tabular}
  \caption{\small Details of the cut-flow of the present analysis in the boosted, intermediate
    and resolved categories.
    %
    See text for more details.
    \label{tab:cutflowdetails}
  }
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In Fig.~\ref{fig:histoBack} we show the decomposition of the background for one important kinematical
distribution, the $p_T$ of the leading reconstructed Higgs candidate, various background
components, for both the boosted and the resolved categories.
%
In the same figure we also show the results of the corresponding comparison
at the level of the $p_T^{hh}$ of the
reconstructed di-Higgs system.
%
The histograms correspond to the distributions at the end of the cut-based
analysis.
%
The results are consistent with those summarized
before in the boosted case we see how $4b$ is the most important
component of the background, with $2b2j$ being of the same order of magnitude, while
for the resolved category we see that $2b2j$ dominates instead.
%
So the effect of the fakes is certainly important, but fortunately it is not a limiting factor
in the resolved category, the one that leads to higher signal significance.
